---
title: "Interior optimum of first-period precision $h_1^\\ast$"
author: "Diwen Si"
format:
  html:
    toc: true
    code-fold: false
    embed-resources: false
execute:
  warning: false
  message: false
---

## Setup

Shared helpers (closed-form $P_{T=2}$, calibration baselines, perturbation list)
live in `utils.R`. The main script reproduces the grid sweep and perturbation
table reported in Section 4 of the thesis.

```{r setup}
source("utils.R")
```

```{r core-function}
# Promotion probability with arbitrary eta*, T = 2.
P_T2_general <- function(h1, eta_star, B, h_eta, h_L, h_H) {
  sigma1 <- sqrt(h1 / (h_eta * (h_eta + h1)))
  tau2_H <- sqrt(h_H / ((h_eta + h1) * (h_eta + h1 + h_H)))
  tau2_L <- sqrt(h_L / ((h_eta + h1) * (h_eta + h1 + h_L)))

  z_star <- (eta_star - B) / sigma1

  integrand_H <- function(z) {
    hat_eta_1 <- B + z * sigma1
    (1 - pnorm((eta_star - hat_eta_1) / tau2_H)) * dnorm(z)
  }
  integrand_L <- function(z) {
    hat_eta_1 <- B + z * sigma1
    (1 - pnorm((eta_star - hat_eta_1) / tau2_L)) * dnorm(z)
  }

  val_H <- integrate(integrand_H, lower = -Inf, upper = z_star)$value
  val_L <- integrate(integrand_L, lower = z_star, upper = Inf)$value
  val_H + val_L
}
```

## Grid sweep in $\eta^\ast$

Vary the promotion threshold $\eta^\ast$ around the prior mean $B = 0.4$ and
record the maximiser $h_1^\ast$ on $[h_L, h_H]$.

```{r grid-sweep}
B       <- 0.4
h_eta   <- 1.0
h_L     <- 0.5
hH_vals <- c(2.0, 5.0)

all_results <- list()

for (j in seq_along(hH_vals)) {
  h_H <- hH_vals[j]

  cat(sprintf("\nParameters: B = %.1f, h_eta = %.1f, h_L = %.1f, h_H = %.1f\n\n",
              B, h_eta, h_L, h_H))

  eta_grid <- seq(B - 0.5, B + 0.5, length.out = 101)
  results  <- data.frame(eta_star = eta_grid, delta = eta_grid - B,
                         h1_star = NA, P_prom = NA)

  cat(sprintf("%10s %10s %10s %10s\n", "eta*", "delta", "h1*", "P_prom"))
  cat(strrep("-", 45), "\n", sep = "")

  for (i in seq_along(eta_grid)) {
    e_star <- eta_grid[i]
    res <- optimize(function(h1) P_T2_general(h1, e_star, B, h_eta, h_L, h_H),
                    interval = c(h_L, h_H), maximum = TRUE, tol = 1e-6)
    results$h1_star[i] <- res$maximum
    results$P_prom[i]  <- res$objective

    if (i %% 5 == 1) {
      cat(sprintf("%10.3f %10.3f %10.4f %10.4f\n",
                  e_star, results$delta[i], res$maximum, res$objective))
    }
  }

  all_results[[j]] <- results
}
```

### LaTeX table at five focal thresholds

```{r latex-table-1}
eta_select <- c(0.90, 0.95, 1.00, 1.05, 1.10)

get_vals <- function(df, vals) {
  idx <- match(round(vals, 4), round(df$eta_star, 4))
  df$h1_star[idx]
}

row_h2 <- get_vals(all_results[[1]], eta_select)
row_h5 <- get_vals(all_results[[2]], eta_select)

latex_lines <- c(
  "\\begin{center}",
  "\\begin{tabular}{lccccc}",
  "\\toprule",
  "$h_H$ & $0.90$ & $0.95$ & $1.00$ & $1.05$ & $1.10$ \\\\",
  "\\midrule",
  paste0("$h_1^*(h_H = 2)$ & ",
         paste(sprintf("%.4f", row_h2), collapse = " & "), " \\\\"),
  paste0("$h_1^*(h_H = 5)$ & ",
         paste(sprintf("%.4f", row_h5), collapse = " & "), " \\\\"),
  "\\bottomrule",
  "\\end{tabular}",
  "\\end{center}"
)

cat(paste(latex_lines, collapse = "\n"), "\n")
```

## Perturbation analysis at $\eta^\ast = B$

Closed-form maximiser cross-checked against `integrate()`-based numerical
optimisation. An "interior" verdict means $h_1^\ast \in (h_L, h_H)$ to within
$10^{-4}$.

```{r perturbations}
cals <- c(list(baseline = baseline), perturbations)

cat(sprintf("%-12s %5s %5s %5s %5s   %8s %8s   %10s   %s\n",
            "label", "B", "h_eta", "h_L", "h_H",
            "h1*_cf", "h1*_opt", "P*", "interior"))
cat(strrep("-", 90), "\n", sep = "")

pert_rows <- list()
for (lab in names(cals)) {
  cal <- cals[[lab]]

  cf <- optimize(function(h) P_T2(h, cal$h_L, cal$h_H, cal$h_eta),
                 interval = c(cal$h_L, cal$h_H), maximum = TRUE, tol = 1e-10)

  og <- optimize(function(h) P_T2_general(h, cal$B, cal$B, cal$h_eta,
                                          cal$h_L, cal$h_H),
                 interval = c(cal$h_L, cal$h_H), maximum = TRUE, tol = 1e-8)

  eps <- 1e-4
  interior <- if (cf$maximum < cal$h_L + eps) "corner @ h_L"
              else if (cf$maximum > cal$h_H - eps) "corner @ h_H"
              else "yes"

  cat(sprintf("%-12s %5.2f %5.2f %5.2f %5.2f   %8.5f %8.5f   %10.7f   %s\n",
              lab, cal$B, cal$h_eta, cal$h_L, cal$h_H,
              cf$maximum, og$maximum, cf$objective, interior))

  pert_rows[[lab]] <- list(B = cal$B, h_eta = cal$h_eta,
                           h_L = cal$h_L, h_H = cal$h_H,
                           h1_star = cf$maximum, P_star = cf$objective,
                           interior = interior)
}
```

### LaTeX table for the perturbation panel

```{r latex-table-2}
fmt_row <- function(lab, r) {
  interior_str <- if (r$interior == "yes") "yes"
                  else if (r$interior == "corner @ h_L") "no (corner at $\\underline h$)"
                  else "no (corner at $\\bar h$)"
  sprintf("%s & %.1f & $(%.2f,\\,%.2f)$ & %.4f & %s \\\\",
          lab, r$h_eta, r$h_L, r$h_H, r$h1_star, interior_str)
}

pert_latex_lines <- c(
  "\\begin{table}",
  "\\centering",
  "\\caption{Optimal first-period precision at $\\eta^*=B$, single-parameter perturbations (continuous solver).}",
  "\\label{tab:simA_compstat}",
  "\\begin{tabular}{lcccc}",
  "\\toprule",
  "Perturbation & $h_\\eta$ & $(\\underline h,\\bar h)$ & $h_1^*$ & Interior \\\\",
  "\\midrule",
  vapply(names(pert_rows), function(lab) fmt_row(lab, pert_rows[[lab]]),
         character(1)),
  "\\bottomrule",
  "\\end{tabular}",
  "\\end{table}"
)

cat(paste(pert_latex_lines, collapse = "\n"), "\n")
```
